HCM SCD risk algorithm cost-effectiveness analysis

### 2021-07-21 HCM.SCD.CEanalysis/inst/rmarkdown/draft.Rmd
check that probabilities look sensible and written ggplot version of trans probs histograms

Figure \@ref(fig:hist) gives a histogram of posterior distributions for state transition probabilities.

```{r hist, fig.align="center", echo=FALSE, out.width = "80%", fig.cap="Histogram of posterior distributions for state transition probabilities."}
knitr::include_graphics("posterior_histograms.png")
```

>>>>

Figures \@ref(fig:histnoICD) and \@ref(fig:histICD) give histograms of posterior distributions for state transition probabilities for no groups without and with ICD implants.

```{r histnoICD, fig.align="center", echo=FALSE, out.width = "80%", fig.cap="Histogram of posterior distributions for state transition probabilities."}
knitr::include_graphics("../../images/post_hist_noICD.png")
```

```{r histICD, fig.align="center", echo=FALSE, out.width = "80%", fig.cap="Histogram of posterior distributions for state transition probabilities."}
knitr::include_graphics("../../images/post_hist_withICD.png")
```

### 2021-07-21 HCM.SCD.CEanalysis/inst/rmarkdown/draft.tex
check that probabilities look sensible and written ggplot version of trans probs histograms

Figure \ref{fig:hist} gives a histogram of posterior distributions for state transition probabilities.

@@

{\centering \includegraphics[width=0.8\linewidth]{posterior_histograms}

@@

\caption{Histogram of posterior distributions for state transition probabilities.}\label{fig:hist}
\end{figure}

>>>>

Figures \ref{fig:histnoICD} and \ref{fig:histICD} give histograms of posterior distributions for state transition probabilities for no groups without and with ICD implants.

@@

{\centering \includegraphics[width=0.8\linewidth]{../../images/post_hist_noICD}

@@

\caption{Histogram of posterior distributions for state transition probabilities.}\label{fig:histnoICD}
\end{figure}

{\centering \includegraphics[width=0.8\linewidth]{../../images/post_hist_withICD}

\caption{Histogram of posterior distributions for state transition probabilities.}\label{fig:histICD}
\end{figure}
